---
title: "Brazil Tourism Employment Analysis"
output: pdf_document
---



Conduct differnce in means test on the linear trend of Rio vs Brazil tourism jobs post the janurary 2016 peak. (Data brough over from python notebook)

```{r}


Differenced_Data_Brazil = c(-0.02503221, -0.02900012, -0.08011404, -0.01252862,  0.00611218,
        0.02210225,  0.06874277, -0.09075547,  0.01170731,  0.01106027,
        0.02054051,  0.10256966, -0.03697156, -0.02391241, -0.08551949,
       -0.00620461,  0.00309172,  0.02390663,  0.07235442, -0.09674152,
        0.01159754,  0.01301101,  0.01906253,  0.10163665, -0.03546759,
       -0.02697332, -0.08190591, -0.00408056,  0.00126904,  0.02237378,
        0.07004839, -0.09351597,  0.01201061,  0.01317951,  0.01907408,
        0.10276415)

Differenced_Data_Rio = c(-0.03457079, -0.02203888, -0.07188065, -0.0127779 ,  0.01459286,
        0.02071588,  0.07660089, -0.10316722,  0.01272471, -0.00079779,
        0.01785714,  0.10971572, -0.06016647, -0.0219591 , -0.08711839,
       -0.00952691,  0.00164211,  0.01609536,  0.05835815, -0.09923146,
        0.01269147,  0.00164211,  0.01594245,  0.10328688, -0.05091879,
       -0.021394  , -0.07353606, -0.0078848 ,  0.00427481,  0.01549702,
        0.05541299, -0.09330789,  0.01473248,  0.003005  ,  0.01660063,
        0.10203702)


```

Check Seasonality using periodogram
```{r}
n <- length(Differenced_Data_Brazil)

plot(1:(n/2),abs(fft(Differenced_Data_Brazil)[2:(n/2+1)])^2/n,type ='h', main ='Spectral Estimate',xlab= 'Frequency' )
plot(1:(n/2),abs(fft(Differenced_Data_Rio)[2:(n/2+1)])^2/n,type ='h', main ='Spectral Estimate',xlab= 'Frequency' )

```

check stationary via augmented Dick-FUller test

```{r}
library(tseries)
adf_test <- adf.test(Differenced_Data_Brazil, alternative = 'stationary')
adf_test
```

Modeling the % change in tourism emplyment since the peak of the market in janurary.  The Data has been differenced to make it stationary, we will conduct a hypothesis test that the mean % decline in the Brazil data is different thatn the rio data.  In order to do this we will model the stationary time series as a MA(7) model, which was selected based on AIC score. Once we assume normality of erros we can proceed with inference on the average % decline in tourism employment unemployment. We will test the hypothsis that:
$$\mu_0 = m_1 $$ where $\mu_0$ is the mean % employment change from the peak for the Rio data and $\mu_1$ is the mean % employment change from the peak for the total Brazil data.

Note, an MA model is always stationary so Augmented Dick Fuller test not neccessary

```{r}

library('forecast')

lines(Differenced_Data_Rio,col='2')



#checking AIC Score for model fit
for(j in 7:7){
  model = arima(Differenced_Data_Rio, order = c(0,0,j),seasonal =list(order = c(0,0,j), period = 12))
  print(paste0('Rio Data, MA order: ',j,' Aic:',model$aic))
  model2 = arima(Differenced_Data_Brazil,order = c(0,0,j),seasonal =list(order = c(0,0,j), period = 12))
   print(paste0('Brazil Data, MA order: ',j,' Aic:',model2$aic))
  



#fit MA(7) model
  model = arima(Differenced_Data_Rio, order = c(0,0,j),seasonal =list(order = c(0,0,j), period = 12))
  
  model2 = arima(Differenced_Data_Brazil,order = c(0,0,j),seasonal =list(order = c(0,0,j), period = 12))
  
  
  #Constructin hypothesis test for difference in means
  mu <- model$coef[2*j+1] - model2$coef[2*j+1]
  s_e <- sqrt(model$var.coef[2*j+1,2*j+1]/length(Differenced_Data_Rio) + model2$var.coef[2*j+1,2*j+1]/length(Differenced_Data_Brazil))
  
  if(mu< (-s_e*1.65)){
    
    print('Reject Null')
    
  }else{
    
    print('Maintain Null')
  }

}
forecast = predict(model,length(Differenced_Data_Brazil))
forecast2 = predict(model,length(Differenced_Data_Rio))
plot(1:length(Differenced_Data_Brazil),Differenced_Data_Brazil, type = 'l',main='Brazil tourism % employment Change from peak + MA(7) fit')
lines(1:length(Differenced_Data_Brazil), forecast$pred,col='3')
plot(1:length(Differenced_Data_Rio),Differenced_Data_Rio, type = 'l',main='Rio tourism % employment Change from peak + MA(7) fit')
lines(1:length(Differenced_Data_Rio), forecast2$pred,col='3')

```
